\textbf{Analyzing Machupo virus-receptor binding by molecular dynamics simulations}

### 2014-01-05 paper.tex
Added a lot of data and scripts as well as many manuscript updates.

Despite, the fact that viral binding occurs at the site of a flexible loop in the free hTfR structure, our data shows after binding the strand is extremely rigid. None of the sites in the interfacial strand have root mean squared fluctuation (RMSF) values in the top half of all sites in the complex during equilibration (Figure~\ref{fig:rmsf}). This is unsurprising considering the high degree of burial that occurs as a result of viral binding. In addition, computing the root mean squared deviation (RMSD) of the entire structure over the trajectory shows that none of the mutations are so deleterious as the cause rapid unbinding. In fact, the RMSD over trajectory looks incredibly invariant across mutants (Figure~\ref{fig:rmsd}).

@@

\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=6in]{figures/rmsfs.pdf}}
\caption{\label{fig:rmsf}\title{RMSF values.} The RMSF values for every site in the bound complex computed during the equilibration phase of the protocol. Each color represents the average over 20 trajectories of a single mutant. The plot shows the flexibility of each site is essentially independent of mutation, and none of the sites above 0.72~\AA\ are found in the interface.}
\end{figure}

\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=6in]{figures/rmsds.pdf}}
\caption{\label{fig:rmsd}\title{RMSD values.} The RMSD values over the time of the trajectory computed during the equilibration phase of the protocol. Each color represents the average over 20 trajectories of a single mutant. The plot shows none of the mutants causes immediate unbinding of the protein--protein complex. In addition, the universal upward trend near the end of the equilibration trajectories may indicate the crystal is more tightly packed than would normally occur in solution.}
\end{figure}

>>>>

Despite, the fact that viral binding occurs at the site of a flexible loop in the free hTfR structure, our data shows after binding the strand is extremely rigid. All two sites had receptor strand have root mean squared fluctuation (RMSF) values in the top half of all receptor sites during equilibration (Figure~\ref{fig:rmsf}), and those are almost completely exposed to solvent. This is unsurprising considering the high degree of burial that occurs as a result of viral binding. Computing the root mean squared deviation (RMSD) of the entire structure over the trajectory shows that none of the mutations are so deleterious as the cause rapid unbinding. In fact, the RMSD over trajectory looks incredibly invariant across mutants (Figure~\ref{fig:rmsd}). By comparison to the equilibration RMSF calculation, near the end of the SMD trajectory all of the residues in the WT receptor interfacial strand are in the top half of RMSF over all receptor sites (Figure~\ref{fig:rmsf_comparison}). Thus, if sufficient simulation time is not dedicated to allowing this unfolding process, standard free energy techniques may miss the energetic contributions that result from ordering the flexible loop in the hTfR apical domain.

@@

\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=6in]{figures/rmsfs.pdf}}
\caption{\label{fig:rmsf}\title{RMSF values during equilibration.} The RMSF values for every site in the bound complex computed during the equilibration phase of the protocol. Each color represents the average over 20 trajectories of a single mutant. Indices 17-25 are the hTfR flexible loop. The plot shows the flexibility of each site is essentially independent of mutation, and two sites above 0.72~\AA\ are found on the receptor in the interface.}
\end{figure}

\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=6in]{figures/rmsds.pdf}}
\caption{\label{fig:rmsd}\title{RMSD values during equilibration.} The RMSD values over the time of the trajectory computed during the equilibration phase of the protocol. Each color represents the average over 20 trajectories of a single mutant. The plot shows none of the mutants causes immediate unbinding of the protein--protein complex. In addition, the universal upward trend near the end of the equilibration trajectories may indicate the crystal is more tightly packed than would normally occur in solution.}
\end{figure}

\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=6in]{figures/rmsf_comparison.pdf}}
\caption{\label{fig:rmsf_comparison}\title{RMSF values of WT hTfR in equilibration and SMD.} The RMSF values for every site in the WT receptor were computed during the equilibration phase and during final 50 frames of the SMD trajectories. The black line was computed over equilibration and the red line during SMD. The plot shows the solution mobility of the hTfR flexible loop increases more than the average during the unbinding process.}
\end{figure}
